Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 overall.tex
minor fixes to language, space saving etc.

In September 2016, increasing the number of concurrent PanDA brokers from 4
to 20 markedly improved efficiency (see Fig.~\ref{fig:backfill-utilization})
but further research is undergoing to understand whether an even larger
number of brokers would yield similar results. This research focuses on
evaluating the overheads of input/output files staging, including its impact
on DTNs, and on an alternative design of PanDA Broker that enables the
concurrent submission of multiple MPI scripts~\cite{barreiro2016panda}. The
results of these investigation will contribute to improve the efficienty of
PanDA Brokers beyond the 30\% limit showed in
Fig.~\ref{fig:backfill-utilization}.

@@

We use two main parameters to measure the performance of the detector
simulation jobs submitted to Titan: (i) the time taken to setup AthenaMP\@;
and (ii) the distribution of the time taken by the Geant4 toolkit to simulate
a certain number of events.

>>>>

In September 2016, increasing the number of concurrent PanDA brokers from 4
to 20 markedly improved efficiency (see Fig.~\ref{fig:backfill-utilization})
but further research is ongoing to understand whether an even greater
number of brokers would yield even greater efficiency. This research focuses on
evaluating the overheads of input/output files staging, including its impact
on DTNs, and on an alternative design of PanDA Broker that enables the
concurrent submission of multiple MPI scripts~\cite{barreiro2016panda}. The
understanding will contribute to improving the efficiency of
PanDA Brokers beyond the 30\% limit showed in
Fig.~\ref{fig:backfill-utilization}.

@@

We use two main parameters to measure the performance of the detector
simulation jobs submitted to Titan: (i) the time taken to setup AthenaMP\@;
and (ii) the distribution of the time taken by Geant4 to simulate
a certain number of events.
